\Large \bf 6.824 Final Project

### 2014-05-10 writeup/paper.tex
paper edits
added some charts....last commit before bed

\begin{table}[h]
\begin{tabular}{|l|l|l|l|}
\hline
\multicolumn{4}{|c|}{\cellcolor[HTML]{C0C0C0}{\color[HTML]{000000} \textbf{Vanilla Paxos}}}                              \\ \hline
                              & \textbf{Avg. Client Latency} & \textbf{Avg. Client Thruput} & \textbf{System Thruput} \\ \hline
\multicolumn{4}{|c|}{\textit{PutHash to one key}}                                                                     \\ \hline
\textbf{1 group, 3 replicas}  & 21.6ms/op                    & 46 requests/s                & 85 requests/s           \\ \hline
\textbf{1 group, 10 replicas} & 52.7ms/op                    & 19 requests/s                & 19 requests/s           \\ \hline
\textbf{3 groups, 3 replicas} & 15.4ms/op                    & 65 requests/s                & 70 requests/s           \\ \hline
\multicolumn{4}{|c|}{\textit{PutHash to many keys}}                                                                 \\ \hline
\textbf{1 group, 3 replicas}  & 20.5ms/op                    & 49 requests/s                & 78 requests/s           \\ \hline
\textbf{1 group, 10 replicas} & 74ms/op                      & 14 requests/s                & 19 requests/s           \\ \hline
\textbf{3 groups, 3 replicas} & 21.8ms/op                    & 46 requests/s                & 179 requests/s          \\ \hline
\end{tabular}
\end{table}

@@

@@

\section{Conclusion}

>>>>

These charts need to be re-done, numbers were off because of a code bug.
\begin{table}[h]
\begin{tabular}{|l|l|l|l|}
\hline
\multicolumn{4}{|c|}{\cellcolor[HTML]{C0C0C0}{\color[HTML]{000000} \textbf{Vanilla Paxos}}}                              \\ \hline
                              & \textbf{Avg. Client Latency} & \textbf{Avg. Client Thruput} & \textbf{System Thruput} \\ \hline
\multicolumn{4}{|c|}{\textit{PutHash to one key}}                                                                     \\ \hline
\textbf{1 group, 3 replicas}  & 21.6ms/op                    & 46 requests/s                & 85 requests/s           \\ \hline
\textbf{1 group, 10 replicas} & 52.7ms/op                    & 19 requests/s                & 19 requests/s           \\ \hline
\textbf{3 groups, 3 replicas} & 15.4ms/op                    & 65 requests/s                & 70 requests/s           \\ \hline
\multicolumn{4}{|c|}{\textit{PutHash to many keys}}                                                                 \\ \hline
\textbf{1 group, 3 replicas}  & 20.5ms/op                    & 49 requests/s                & 78 requests/s           \\ \hline
\textbf{1 group, 10 replicas} & 74ms/op                      & 14 requests/s                & 19 requests/s           \\ \hline
\textbf{3 groups, 3 replicas} & 21.8ms/op                    & 46 requests/s                & 179 requests/s          \\ \hline
\end{tabular}
\end{table}

@@

\begin{figure}[H]
\centering
\makebox[\textwidth][c]{
\includegraphics[scale=.66]{replicas.png}}
\caption{Performance of a one-group configuration rapidly dteriorates as the number of replicas increases}
\label{fig:replicas}
\end{figure}

\begin{figure}[H]
\centering
\makebox[\textwidth][c]{
\includegraphics[scale=.66]{groups.png}}
\caption{Performance increases linearly as the number of groups increases. There is probably a saturation point, but we didn't have enough cluster machines to reach it.}
\label{fig:groups}
\end{figure}

@@

\section{Conclusion}
We did a project.
